---
output: html_document
---

<!-- Setup -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

files.source <- list.files("SupportCode", pattern = "\\.R")
sapply(paste0("SupportCode\\",files.source),source)

# Read in all DefinitionInformationTable excel sheets into a single, named list.
DefinitionInformation <- multiplesheets(fname = "DefinitionInformationTable.xlsx")

query_start <- DefinitionInformation[["Setup"]]$StartDate %>% as.Date()
query_end <- DefinitionInformation[["Setup"]]$EndDate %>% as.Date()
jurisdiction <- DefinitionInformation[["Setup"]]$Jurisdiction

select_fields <- DefinitionInformation[["AppliedFields"]] %>% pull_no_na(df=., variable = "Field")
deduplicate_ddx <- DefinitionInformation[["ValidationReviewInformation"]] %>% pull_no_na(df=., variable = "DeduplicateDDx")

# Define Output Folder 
output_folder <- "Output_OneDef\\"

```

<!-- Def1 -->

```{r def1_setup, echo=FALSE, message=FALSE, warning=FALSE}

def1_table <- DefinitionInformation[["DefinitionInformation"]] %>% filter(defX == "def1")

def1_name <- def1_table$Syndrome
def1_short <- def1_table$Abbreviation
def1_structure <- clean_query_essence(def1_table$Structure)
def1_structure_print <- def1_table$Structure %>%
  str_replace_all(., pattern = "\\^", replacement = "\\\\^") %>%
  str_replace_all(., pattern = "\\_", replacement = "\\\\_") # Prevents R Markdown from interpreting "_" as start/end of bold commands.
def1_url <- def1_table$API

```

```{r def1_extract, echo=FALSE, message=FALSE, warning=FALSE}

def1_full <- get_longterm_details(url = def1_url, start_date = query_start, end_date = query_end)

def1 <- def1_full %>%
  dplyr::select(Date, EssenceID, select_fields)  %>%
  mutate(def1 = 1) %>%
  mutate(Date = as.Date(Date, format='%m/%d/%Y')) %>%
  filter(Date >= query_start) %>%
  filter(Date <= query_end) 

if(deduplicate_ddx == TRUE){def1 <- def1 %>% dedup_dx(df=., keep_raw = FALSE)}

def1_total <- nrow(def1)
def1_total_pretty <- format(def1_total, big.mark = ",", scientific = FALSE)

```

```{r def1_elements, echo=FALSE, message=FALSE, warning=FALSE}

def1_elements <- (def1_structure$`Syndrome Element`)

def1_elements_detected <- def1 %>%
  dplyr::select(EssenceID, ChiefComplaintParsed, DischargeDiagnosis) %>%
  clean_ChiefComplaintParsed() %>%
  clean_DischargeDiagnosis() %>%
  mutate(CCDDclean = paste(ChiefComplaintParsed, DischargeDiagnosis)) %>%
  select(EssenceID, CCDDclean) %>%
  detect_elements(data = ., def1_elements, text_field = "CCDDclean") %>%
  janitor::adorn_totals(where = "row")

def1_elements_detected_table <- def1_elements_detected %>%
  select(-TruePositive, -CCDDclean) %>%
  filter(EssenceID=="Total") %>%
  pivot_longer(cols = starts_with("element"), names_to = "Syndrome Element", values_to = "VisitsMatched") %>%
  mutate(`Syndrome Element` = str_remove(`Syndrome Element`,"element_")) %>%
  mutate(`Syndrome Element` = str_replace_all(`Syndrome Element`, "\\."," ")) %>%
  full_join(def1_structure) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="Diagnosis Code", str_to_sentence(`Syndrome Element`), `Syndrome Element`)) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="CCDD Category (see ESSENCE)", is.na(`Syndrome Element`), `Syndrome Element`)) %>%
  select(`Syndrome Element`, `Element Type`, `CCDD Matches` = VisitsMatched) %>%
  arrange(desc(`CCDD Matches`))

```

---
title: "Definition Evaluation: `r def1_name`"
author: `r query_start` to `r query_end`
---  
  
**Jurisdiction**: `r jurisdiction`  
**Report Created**: `r Sys.Date()`    
**Point of Contact**: `r DefinitionInformation[["Setup"]]$PointOfContact` (`r DefinitionInformation[["Setup"]]$POCEmail`)    
**Organization**: `r DefinitionInformation[["Setup"]]$Organization`



***  
### Individual Definition Information  
  
Inclusion terms and codes are displayed in the table below (exclusion terms are not shown in the table). Visits may match on multiple syndrome elements. Refer to the csv outputs for visit-level information about which visits matched on which elements.  
  
#### `r def1_name` (`r def1_short`)   
  
**Total Visits Identified:**  
  
`r def1_total_pretty`  
  
**Query description:**    
  
`r def1_table$Description`  
  
**Full query:**  
`r def1_structure_print`  
  
```{r def1_table, echo=FALSE, message=FALSE, warning=FALSE}

DT::datatable(def1_elements_detected_table, rownames = FALSE, options = list(pageLength = nrow(def1_structure), dom = "t"), filter = "top", escape = FALSE)

```
  
  
#### Visits over time     
  
Use the slider at the bottom of the figures to adjust the start and end dates visible in the graph.   
  
```{r time_series, echo=FALSE, message=FALSE, warning=FALSE}

fill_dates <- data.frame(Date = seq.Date(from = as.Date(query_start), to = as.Date(query_end), by = "day"))

time_series_def1 <- def1 %>%
  dplyr::count(Date, name = "Visits") %>%
  filter(Date<=query_end) %>%
  full_join(fill_dates) %>%
  mutate(Syndrome = def1_short) %>%
  arrange(Date) %>%
  replace_na(list(Visits = 0))

plot_ly() %>%
  add_lines(data = time_series_def1,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(226,78,66)')) %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(query_start,query_end),
      rangeslider = list(type = "date", thickness = 0.1))
  )


```

  
***   
### Top terms (besides "patient")
#### Top 5 occurring terms for each definition and each field of interest:

```{r word_prep, echo=FALSE, message = FALSE, warning = FALSE, results='hide'}

my_file <- def1 %>%
  mutate(Date = mdy(Date))

my_file <- clean_Admit_Reason_Combo()
my_file <- clean_ChiefComplaintOriginal()
my_file <- clean_ChiefComplaintUpdates()
my_file <- clean_ChiefComplaintParsed()
my_file <- clean_CCDD()
my_file <- clean_DischargeDiagnosis()
my_file <- clean_TriageNotesOrig()


```

```{r top_terms, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}

def_sets <- list(my_file[my_file$def1==1,])

def_sets_names <- c(def1_short)

top_words <- list()
word_count <- list()

for (i in 1:length(def_sets)) {
  
  for(j in 1:length(select_fields)) {
    
    data <- as.data.frame(def_sets[i])
    
    field <- select_fields[j]
    
    word_count[[j]] <- data %>%
      dplyr::select(field) %>%
      unnest_tokens(word, !!field) %>%
      anti_join(stop_words, by = "word") %>%
      dplyr::count(word, name = "Count", sort=TRUE) %>%
      filter(word!="patient") %>%
      top_n(5) %>%
      mutate(def = def_sets_names[i],
             field = field)

    names(word_count)[[j]] <- select_fields[j]  
    
    }
  
  top_words[[i]] <- plyr::ldply(word_count, data.frame)

  names(top_words)[[i]] <- def_sets_names[i]
  
}

top_words_combined <- ldply(top_words, data.frame) %>%
  dplyr::arrange(Count) %>%
  group_by(def,field) %>%
  dplyr::mutate(order = row_number())

ggplot(data = top_words_combined) +
  geom_bar(aes(x = Count, y = as.factor(order)), stat="identity", fill = "#a4dba4") +
  geom_text(aes(x = 0, y = as.factor(order), label = paste0(word,'  (',Count,")"), hjust = "left"), size = 3) + 
  facet_grid(field ~ def, switch = "y", scales = "free") +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    panel.grid = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    panel.background = element_rect(fill = NA, color = "grey40"),
    axis.title = element_blank()
  )

```

<!-- Writing Linelists -->

```{r output, echo=FALSE, message=FALSE, warning=FALSE}

# All Visits
write.csv(file = paste0(output_folder,def1_short," All Visits.csv"),
          x = def1,
          row.names = FALSE)

# Create Matched Elements Subfolder
fs::dir_create(paste0(output_folder, "Matched_Elements"))

# Def1 matched elements
write.csv(file = paste0(output_folder,"Matched_Elements\\",def1_short," Matched Elements.csv"),
          x = def1_elements_detected,
          row.names = FALSE)


```

<!-- Validation Review -->

```{r validation review setup, include=FALSE}

validation_review <- DefinitionInformation[["Setup"]]$ValidationReview


if(validation_review == TRUE){

## Identify # of Reviewers
n_reviewers <- DefinitionInformation[["ValidationReviewInformation"]]$ReviewerID %>% max()

# ## Identify Definitions to be Reviewed
validation_review_defs <- c("def1") # Change based on Evaluation Template #

## Establish Sampling Parameters
SampleMetric <- DefinitionInformation[["ValidationReviewInformation"]] %>% pull_no_na(df=., variable = "SampleMetric")
SampleValue <- DefinitionInformation[["ValidationReviewInformation"]] %>% pull_no_na(df=., variable = "SampleValue")
StratifiedSample <- DefinitionInformation[["ValidationReviewInformation"]] %>% pull_no_na(df=., variable = "StratifiedSample")
StratifiedVariables <- DefinitionInformation[["ValidationReviewInformation"]] %>% 
  pull_no_na(df=., variable = "StratifiedVariables") %>% # Pull StratifiedVariables (remove NAs)
  strsplit(., split = ",") %>% # Split single string "A, B" into a string vector c("A"," B") using the comma
  unlist() %>%  # Unlist (strsplit() puts new vector into a list)
  str_trim(., side="both") # Remove all whitespace on every string in the string vector: c("A", " B") --> c("A","B")

# Establish Review Scale
ReviewScaleLow <- DefinitionInformation[["ValidationReviewInformation"]]$ReviewScaleLow[1]
ReviewScaleHigh <- DefinitionInformation[["ValidationReviewInformation"]]$ReviewScaleHigh[1]

}
```

```{r validation review file directories, include=FALSE}
if(validation_review == TRUE){

## Create Validation Review File Directories

for(i in seq_along(validation_review_defs)){ # for each definition specified (i) create the following filepaths
  
  # Step 1: Create folder name for each definition undergoing validation review
  def_review_folder <- name_def_review_folder(definition = validation_review_defs[i])

  # Step 2: Create folders for each stage of a definition's validation review process
  fs::dir_create(paste0(output_folder, "Validation_Review\\",def_review_folder,"\\Resources"))
  fs::dir_create(paste0(output_folder, "Validation_Review\\",def_review_folder,"\\1_Reviewed_Data"))
  
  if(n_reviewers > 1){ # Only create consensus data folders if > 1 reviewer.
      fs::dir_create(paste0(output_folder, "Validation_Review\\",def_review_folder,"\\2_Consensus_Data"))
  }

  # Step 3: Create subfolders for each reviewer examining a definition
  for(j in 1:n_reviewers){ # for each reviewer specified (j) create reviewer specific subfolder (within each definition being reviewed)
    
  fs::dir_create(paste0(output_folder, "Validation_Review\\",def_review_folder,"\\1_Reviewed_Data\\Reviewer_",j))
    }
  }
rm(def_review_folder)
}
```

```{r validation reviewer files, include=FALSE}
if(validation_review == TRUE){

# Development Note: I will attempt to keep all Reviewer columns the same across IE #'s (Reviewer_TP_## and Reviewer_Notes) and then seek to differentiate these columns across Reviewers after the joining where R will auto-assign .x.y.z etc prefixes. This will likely be easier to work with than generating code to scan a flexible # of uniquely generated var names. 

list <- list()

for(i in seq_along(validation_review_defs)){
  
  # Step 1: Formatting Data for Reviewers
  
  list[[i]] <- get(validation_review_defs[i]) %>%
    distinct(EssenceID, .keep_all = TRUE) %>% # Deduplicate records
    add_date_components(df=.) %>% # Generate Date Components (Date --> Weekday, Week, Month, Year)
    get_sample(df=.,
               sample_metric = SampleMetric,
               sample_value = SampleValue,
               strat_sample = StratifiedSample,
               strat_vars = StratifiedVariables) %>% # SAMPLE
    mutate(Review_Rating = NA,
          Notes = NA) %>%
    ## REORDER VARIABLES: BSI, REVIEWER VARS, EVERYTHING ELSE
    select(Date, EssenceID,
           Review_Rating, Notes,
           everything(),
           -Weekday, -Week, -Month, -Year) %>%
    ## REMOVE ALL CHARACTERS WHICH MAY CAUSE XML ERRORS WITH EXCEL FILES
    mutate(across(.cols = where(is.character), 
                  .fns = ~ str_replace_all(string=., pattern = "[^[:graph:]]", replacement = " "))) # Replace all non-printable characters with a space (to prevent XML encoding issues when writing EXCEL files). 
  
  # Step 2: Create folder name for each definition undergoing validation review
  
  def_review_folder <- name_def_review_folder(definition = validation_review_defs[i])
  
  # Step 3: Save Review Data (1 copy for each reviewer examining each definition)
  
  for(j in 1:n_reviewers){ # for each reviewer specified (j) create reviewer specific subfolder (within each definition being reviewed)
    
    list[[i]] %>%
      writexl::write_xlsx(x=., 
                 path = paste0(output_folder, "Validation_Review\\",def_review_folder,"\\1_Reviewed_Data\\Reviewer_",j,
                             "\\Reviewer_",j,"_Data.xlsx"))
  }
  
  # Step 4: Set up Consensus Review Code for each definition's Validation Review Folder
  
  # Problem: When folks are running SyS Eval_ template, they have not yet started validation review --> so not yet time for Comparison/Consensus process --> need an additional script/button they can run when ready (Consensus_Review.Rmd).
  
  # Step 4a: Create a filepath  for each definition validation review
  filepath <- paste0(output_folder, "Validation_Review\\", def_review_folder)
  
  # Step 4b: Save all parameters needed to run Consensus_Review.Rmd template
  save(filepath, DefinitionInformation,
       file = paste0(filepath,"\\Resources\\Validation_Review_Parameters.RData"))
  
  # Step 4c: Copy Validation Summary R Markdown code template(s) to each definition validation review folder.

  if(n_reviewers == 1){ # Consensus Review not feasible with 1 reviewer --> Singular Validation_Summary.Rmd
  
  file.copy(from = "SupportCode\\Validation_Review\\Validation_Summary.Rmd",
            to = paste0(filepath))
    
  }else if(n_reviewers > 1){ # Only include Post-Consensus Review RMD if there are enough reviewers to do Consensus Review.
    
  # Pre Consensus Review Code Template
  file.copy(from = "SupportCode\\Validation_Review\\Validation_Summary_Pre_Consensus_Review.Rmd",
            to = paste0(filepath))
    
  # Post Consensus Review Code Template
  file.copy(from = "SupportCode\\Validation_Review\\Validation_Summary_Post_Consensus_Review.Rmd",
            to = paste0(filepath))  
    }
  }
}
```
___
*The template for this report was created by Sara Chronister. For questions, ideas for improvement/collaboration, or attribution, please reach out to <sara.chronister@doh.wa.gov>.*