---
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

files.source <- list.files("SupportCode")
sapply(paste0("SupportCode/",files.source),source)

setup_information <- read_excel("DefinitionInformationTable.xlsx", sheet = "Setup", range = "A2:F3")

query_start <- setup_information$StartDate
query_end <- setup_information$EndDate
jurisdiction <- setup_information$Jurisdiction

select_fields_table <- read_excel("DefinitionInformationTable.xlsx", sheet = "AppliedFields", range = "A2:A22") %>%
  filter(!is.na(Field)) 
select_fields <- select_fields_table$Field

information_table <- read_excel("DefinitionInformationTable.xlsx", sheet = "DefinitionInformation", range = "A2:G5")

```

```{r def1_setup, echo=FALSE, message=FALSE, warning=FALSE}

def1_table <- information_table[information_table$defX=="def1",]

def1_name <- def1_table$Syndrome
def1_short <- def1_table$Abbreviation
def1_structure <- clean_query_essence(def1_table$Structure)
def1_structure_print <- str_replace_all(def1_table$Structure,"\\^","\\\\^")
def1_url <- def1_table$API

```

```{r def1_extract, echo=FALSE, message=FALSE, warning=FALSE}

def1_full <- get_longterm_details(url = def1_url, start_date = query_start, end_date = query_end)

def1 <- def1_full %>%
  dplyr::select(Date, EssenceID, select_fields)  %>%
  mutate(def1 = 1) %>%
  mutate(Date = as.Date(Date, format='%m/%d/%Y')) %>%
  filter(Date >= query_start) %>%
  filter(Date <= query_end)

def1_total <- nrow(def1)
def1_total_pretty <- format(def1_total, big.mark = ",", scientific = FALSE)

```

```{r def1_elements, echo=FALSE, message=FALSE, warning=FALSE}

def1_elements <- (def1_structure$`Syndrome Element`)

def1_elements_detected <- def1 %>%
  dplyr::select(EssenceID, ChiefComplaintParsed, DischargeDiagnosis) %>%
  clean_ChiefComplaintParsed() %>%
  clean_DischargeDiagnosis() %>%
  mutate(CCDDclean = paste(ChiefComplaintParsed, DischargeDiagnosis)) %>%
  select(EssenceID, CCDDclean) %>%
  detect_elements(data = ., def1_elements, text_field = "CCDDclean") %>%
  janitor::adorn_totals(where = "row")

def1_elements_detected_table <- def1_elements_detected %>%
  select(-TruePositive, -CCDDclean) %>%
  filter(EssenceID=="Total") %>%
  pivot_longer(cols = starts_with("element"), names_to = "Syndrome Element", values_to = "VisitsMatched") %>%
  mutate(`Syndrome Element` = str_remove(`Syndrome Element`,"element_")) %>%
  mutate(`Syndrome Element` = str_replace_all(`Syndrome Element`, "\\."," ")) %>%
  full_join(def1_structure) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="Diagnosis Code", str_to_sentence(`Syndrome Element`), `Syndrome Element`)) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="CCDD Category (see ESSENCE)", is.na(`Syndrome Element`), `Syndrome Element`)) %>%
  select(`Syndrome Element`, `Element Type`, `CCDD Matches` = VisitsMatched) %>%
  arrange(desc(`CCDD Matches`))

```


```{r def2_setup, echo=FALSE, message=FALSE, warning=FALSE}

def2_table <- information_table[information_table$defX=="def2",]

def2_name <- def2_table$Syndrome
def2_short <- def2_table$Abbreviation
def2_structure <- clean_query_essence(def2_table$Structure)
def2_structure_print <- str_replace_all(def2_table$Structure,"\\^","\\\\^")
def2_url <- def2_table$API

```

```{r def2_extract, echo=FALSE, message=FALSE, warning=FALSE}

def2_full <- get_longterm_details(url = def2_url, start_date = query_start, end_date = query_end)

def2 <- def2_full %>%
  dplyr::select(Date, EssenceID, select_fields) %>%
  mutate(def2 = 1) %>%
  mutate(Date = as.Date(Date, format='%m/%d/%Y')) %>%
  filter(Date >= query_start) %>%
  filter(Date <= query_end)

def2_total <- nrow(def2)
def2_total_pretty <- format(def2_total, big.mark = ",", scientific = FALSE)

```
  
```{r def2_elements, echo=FALSE, message=FALSE, warning=FALSE}

def2_elements <- (def2_structure$`Syndrome Element`)

def2_elements_detected <- def2 %>%
  dplyr::select(EssenceID, ChiefComplaintParsed, DischargeDiagnosis) %>%
  clean_ChiefComplaintParsed() %>%
  clean_DischargeDiagnosis() %>%
  mutate(CCDDclean = paste(ChiefComplaintParsed, DischargeDiagnosis)) %>%
  select(EssenceID, CCDDclean) %>%
  detect_elements(data = ., def2_elements, text_field = "CCDDclean") %>%
  janitor::adorn_totals(where = "row")

def2_elements_detected_table <- def2_elements_detected %>%
  select(-TruePositive, -CCDDclean) %>%
  filter(EssenceID=="Total") %>%
  pivot_longer(cols = starts_with("element"), names_to = "Syndrome Element", values_to = "VisitsMatched") %>%
  mutate(`Syndrome Element` = str_remove(`Syndrome Element`,"element_")) %>%
  mutate(`Syndrome Element` = str_replace_all(`Syndrome Element`, "\\."," ")) %>%
  full_join(def2_structure) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="Diagnosis Code", str_to_sentence(`Syndrome Element`), `Syndrome Element`)) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="CCDD Category (see ESSENCE)", is.na(`Syndrome Element`), `Syndrome Element`)) %>%
  select(`Syndrome Element`, `Element Type`, `CCDD Matches` = VisitsMatched) %>%
  arrange(desc(`CCDD Matches`))

```


```{r def3_setup, echo=FALSE, message=FALSE, warning=FALSE}

def3_table <- information_table[information_table$defX=="def3",]

def3_name <- def3_table$Syndrome
def3_short <- def3_table$Abbreviation
def3_structure <- clean_query_essence(def3_table$Structure)
def3_structure_print <- str_replace_all(def3_table$Structure,"\\^","\\\\^")
def3_url <- def3_table$API

```

```{r def3_extract, echo=FALSE, message=FALSE, warning=FALSE}

def3_full <- get_longterm_details(url = def3_url, start_date = query_start, end_date = query_end)

def3 <- def3_full %>%
  dplyr::select(Date, EssenceID, select_fields) %>%
  mutate(def3 = 1) %>%
  mutate(Date = as.Date(Date, format='%m/%d/%Y')) %>%
  filter(Date >= query_start) %>%
  filter(Date <= query_end)

def3_total <- nrow(def3)
def3_total_pretty <- format(def3_total, big.mark = ",", scientific = FALSE)

```
  
```{r def3_elements, echo=FALSE, message=FALSE, warning=FALSE}

def3_elements <- (def3_structure$`Syndrome Element`)

def3_elements_detected <- def3 %>%
  dplyr::select(EssenceID, ChiefComplaintParsed, DischargeDiagnosis) %>%
  clean_ChiefComplaintParsed() %>%
  clean_DischargeDiagnosis() %>%
  mutate(CCDDclean = paste(ChiefComplaintParsed, DischargeDiagnosis)) %>%
  select(EssenceID, CCDDclean) %>%
  detect_elements(data = ., def3_elements, text_field = "CCDDclean") %>%
  janitor::adorn_totals(where = "row")

def3_elements_detected_table <- def3_elements_detected %>%
  select(-TruePositive, -CCDDclean) %>%
  filter(EssenceID=="Total") %>%
  pivot_longer(cols = starts_with("element"), names_to = "Syndrome Element", values_to = "VisitsMatched") %>%
  mutate(`Syndrome Element` = str_remove(`Syndrome Element`,"element_")) %>%
  mutate(`Syndrome Element` = str_replace_all(`Syndrome Element`, "\\."," ")) %>%
  full_join(def3_structure) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="Diagnosis Code", str_to_sentence(`Syndrome Element`), `Syndrome Element`)) %>%
  mutate(`Syndrome Element` = ifelse(`Element Type`=="CCDD Category (see ESSENCE)", is.na(`Syndrome Element`), `Syndrome Element`)) %>%
  select(`Syndrome Element`, `Element Type`, `CCDD Matches` = VisitsMatched) %>%
  arrange(desc(`CCDD Matches`))

```


---
title: "Definition Evaluation: `r def1_name`, `r def2_name`, and `r def3_name`"
author: `r query_start` to `r query_end`
---  
  
**Jurisdiction**: `r jurisdiction`  
**Report Created**: `r Sys.Date()`    
**Point of Contact**: `r setup_information$PointOfContact` (`r setup_information$POCEmail`)    
**Organization**: `r setup_information$Organization`


***  
### Individual Definition Information  {.tabset}
  
Inclusion terms and codes are displayed in the table below (exclusion terms are not shown in the table)  
  
#### `r def1_name` (`r def1_short`)   
  
**Total Visits Identified:**  
  
`r def1_total_pretty`  
  
**Query description:**    
  
`r def1_table$Description`  
  
**Full query:**  
`r def1_structure_print`  
  
```{r def1_table, echo=FALSE, message=FALSE, warning=FALSE}

DT::datatable(def1_elements_detected_table, rownames = FALSE, options = list(pageLength = nrow(def1_structure), dom = "t"), filter = "top", escape = FALSE)

```
  
#### `r def2_name` (`r def2_short`)   
  
**Total Visits Identified:**  
  
`r def2_total_pretty`  
  
**Query description:**    
  
`r def2_table$Description`  
  
**Full query:**  
`r def2_structure_print`  
  
```{r def2_table, echo=FALSE, message=FALSE, warning=FALSE}

DT::datatable(def2_elements_detected_table, rownames = FALSE, options = list(pageLength = nrow(def2_structure), dom = "t"), filter = "top", escape = FALSE)

```
  
#### `r def3_name` (`r def3_short`)   
  
**Total Visits Identified:**  
  
`r def3_total_pretty`  
  
**Query description:**    
  
`r def3_table$Description`  
  
**Full query:**  
`r def3_structure_print`  
  
```{r def3_table, echo=FALSE, message=FALSE, warning=FALSE}

DT::datatable(def3_elements_detected_table, rownames = FALSE, options = list(pageLength = nrow(def3_structure), dom = "t"), filter = "top", escape = FALSE)

```
  
  
```{r three_defs_prep, echo=FALSE, message=FALSE, warning=FALSE}

join_vars <- c("Date", "EssenceID", select_fields)

three_defs <- full_join(def1, def2, by = join_vars) %>%
  full_join(def3, by = join_vars) %>%
  replace_na(replace = list(def1 = 0, def2 = 0, def3 = 0)) %>%
  mutate(Total_Defs = def1+def2+def3)

Def1_vs_Def2_vs_Def3 <- three_defs
colnames(Def1_vs_Def2_vs_Def3)[which(colnames(Def1_vs_Def2_vs_Def3)=="def1")] <- def1_short
colnames(Def1_vs_Def2_vs_Def3)[which(colnames(Def1_vs_Def2_vs_Def3)=="def2")] <- def2_short
colnames(Def1_vs_Def2_vs_Def3)[which(colnames(Def1_vs_Def2_vs_Def3)=="def3")] <- def3_short

three_defs_table <- three_defs %>%
  mutate(
    # Character values for definition indicator variables
    def1_named = factor(def1, levels = c(0,1), labels = c(paste("Not",def1_short), def1_short)),
    def2_named = factor(def2, levels = c(0,1), labels = c(paste("Not",def2_short), def2_short)),
    def3_named = factor(def3, levels = c(0,1), labels = c(paste("Not",def3_short), def3_short)),
    Total_Defs = factor(Total_Defs, levels = c(1,2,3), labels = c("One Definition", "Two Definitions", "Three Definitions")),
    # Dummy variables for each combination of definitions
    def1_only = ifelse(def1==1&def2==0&def3==0,1,0),
    def1_def2 = ifelse(def1==1&def2==1&def3==0,1,0),
    def1_def3 = ifelse(def1==1&def2==0&def3==1,1,0),
    def2_only = ifelse(def1==0&def2==1&def3==0,1,0),
    def2_def3 = ifelse(def1==0&def2==1&def3==1,1,0),
    def3_only = ifelse(def1==0&def2==0&def3==1,1,0),
    All = ifelse(def1==1&def2==1&def3==1,1,0))


three_defs_table$Definitions <- apply(three_defs_table[,which(colnames(Def1_vs_Def2_vs_Def3)==def1_short):which(colnames(Def1_vs_Def2_vs_Def3)==def3_short)], 1, function(data)
  paste(names(which(data == 1)),collapse = ", "))
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def1",def1_short)
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def2",def2_short)
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def3",def3_short)

three_defs_total <- nrow(three_defs_table)
three_defs_total_pretty <- format(three_defs_total, big.mark = ",", scientific = FALSE)

```
  
  
***  
### Definition Comparison  
  
  
#### Visits by syndrome over time {.tabset}    
  
Use the slider at the bottom of the figures to adjust the start and end dates visible in the graph.   
  
##### Same scale  
  
```{r time_series, echo=FALSE, message=FALSE, warning=FALSE}

fill_dates <- data.frame(Date = seq.Date(from = as.Date(query_start), to = as.Date(query_end), by = "day"))

time_series_def1 <- def1 %>%
  dplyr::count(Date, name = "Visits") %>%
  filter(Date<=query_end) %>%
  full_join(fill_dates) %>%
  mutate(Syndrome = def1_short) %>%
  arrange(Date) %>%
  replace_na(list(Visits = 0))

time_series_def2 <- def2 %>%
  dplyr::count(Date, name = "Visits") %>%
  filter(Date<=query_end) %>%
  full_join(fill_dates) %>%
  mutate(Syndrome = def2_short) %>%
  arrange(Date) %>%
  replace_na(list(Visits = 0))

time_series_def3 <- def3 %>%
  dplyr::count(Date, name = "Visits") %>%
  filter(Date<=query_end) %>%
  full_join(fill_dates) %>%
  mutate(Syndrome = def3_short) %>%
  arrange(Date) %>%
  replace_na(list(Visits = 0))


plot_ly() %>%
  add_lines(data = time_series_def1,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(226,78,66)')) %>%
  add_lines(data = time_series_def2,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(0,143,149)')) %>%
  add_lines(data = time_series_def3,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(233,176,0)')) %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(query_start,query_end),
      rangeslider = list(type = "date", thickness = 0.1))
  )


```
  
##### Independent Scales  
  
```{r ts_separate, echo=FALSE, message=FALSE, warning=FALSE}

ts_plot_def1 <- plot_ly() %>%
  add_lines(data = time_series_def1,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(226,78,66)')) %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(min(fill_dates$Date),max(fill_dates$Date)),
      rangeslider = list(type = "date", thickness = 0.1))
  )

ts_plot_def2 <- plot_ly() %>%
  add_lines(data = time_series_def2,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(0,143,149)')) %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(query_start,query_end),
      rangeslider = list(type = "date", thickness = 0.1))
  )

ts_plot_def3 <- plot_ly() %>%
  add_lines(data = time_series_def3,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = 'rgb(233,176,0)')) %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(query_start,query_end),
      rangeslider = list(type = "date", thickness = 0.1))
  )


subplot(ts_plot_def1, ts_plot_def2, ts_plot_def3, nrows = 3, shareX = TRUE, margin = 0.05)

```
  
  
#### The total number of visits identified by all definitions combined was **`r three_defs_total_pretty`**.   
  
#### Number and percent of all identified visits captured by each definition:        
```{r def_summary, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}

def1_results <- data.frame(Def = def1_name, Count = sum(three_defs_table$def1)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

def2_results <- data.frame(Def = def2_name, Count = sum(three_defs_table$def2)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

def3_results <- data.frame(Def = def3_name, Count = sum(three_defs_table$def3)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

all_def_results <- bind_rows(def1_results, def2_results, def3_results)


ggplot(data = all_def_results, aes(x = Percent, y = reorder(Def,Percent))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=Count, x = Percent-.01), hjust="top", color = "white", size = 3) +
  geom_text(aes(label=Percent.Display, x = Percent+.01), hjust="bottom", color = "black", size = 3) +
  geom_segment(aes(x = 0, xend = 1, y = 0.4, yend = 0.4)) +
  scale_x_continuous(limits = c(0,1.2), expand = c(0,0), breaks = c(0,.25,.50,.75,1), labels = scales::percent_format()) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")


```
  
#### Number and percent of all identified visits captured by each observed combination of definitions: {.tabset}     
  
```{r def_comparison, echo=FALSE, message=FALSE, warning=FALSE}

three_defs_combinations <- data.frame(Definitions = 
                                        c(paste(def1_short,def2_short,sep=", "),
                                          paste(def1_short,def3_short,sep=", "),
                                          paste(def2_short,def3_short,sep=", "),
                                          paste(def1_short,def2_short,def3_short,sep=", "),
                                          paste0(def1_short),
                                          paste0(def2_short),
                                          paste0(def3_short)))

three_defs_summary <- three_defs_table %>%
  dplyr::count(Definitions, name = "Visits") %>%
  mutate(Percent = paste0(round(Visits/sum(Visits)*100,1),"%")) %>%
  full_join(three_defs_combinations) %>%
  replace_na(list(Visits=0,
                  Percent="0%")) %>%
  arrange(desc(Visits))

reactable(three_defs_summary)

```
  
##### Overlap plot, not to scale  
  
```{r venn, echo=FALSE, message=FALSE, warning=FALSE}

plot(venn(Def1_vs_Def2_vs_Def3[,which(colnames(Def1_vs_Def2_vs_Def3)==def1_short):which(colnames(Def1_vs_Def2_vs_Def3)==def3_short)]))

```
  
##### Overlap plot, to scale  
  
```{r euler, echo=FALSE, message=FALSE, warning=FALSE}

plot(euler(Def1_vs_Def2_vs_Def3[,which(colnames(Def1_vs_Def2_vs_Def3)==def1_short):which(colnames(Def1_vs_Def2_vs_Def3)==def3_short)]),quantities = TRUE)

```
  
  
***   
### Top terms (besides "patient")
#### Top 5 occurring terms for each definition and each field of interest:

```{r word_prep, echo=FALSE, message = FALSE, warning = FALSE, results='hide'}

my_file <- three_defs 

my_file <- clean_Admit_Reason_Combo()
my_file <- clean_ChiefComplaintOriginal()
my_file <- clean_ChiefComplaintUpdates()
my_file <- clean_ChiefComplaintParsed()
my_file <- clean_CCDD()
my_file <- clean_DischargeDiagnosis()
my_file <- clean_TriageNotesOrig()


```


```{r top_terms, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}

def_sets <- list(my_file[my_file$def1==1,],
                 my_file[my_file$def2==1,],
                 my_file[my_file$def3==1,])

def_sets_names <- c(def1_short,def2_short,def3_short)

top_words <- list()
word_count <- list()

for (i in 1:length(def_sets)) {
  
  for(j in 1:length(select_fields)) {
    
    data <- as.data.frame(def_sets[i])
    
    field <- select_fields[j]
    
    word_count[[j]] <- data %>%
      dplyr::select(field) %>%
      unnest_tokens(word, !!field) %>%
      anti_join(stop_words, by = "word") %>%
      dplyr::count(word, name = "Count", sort=TRUE) %>%
      filter(word!="patient") %>%
      top_n(5) %>%
      mutate(def = def_sets_names[i],
             field = field)

    names(word_count)[[j]] <- select_fields[j]  
    
    }
  
  top_words[[i]] <- plyr::ldply(word_count, data.frame)

  names(top_words)[[i]] <- def_sets_names[i]
  
}

top_words_combined <- ldply(top_words, data.frame) %>%
  dplyr::arrange(Count) %>%
  group_by(def,field) %>%
  dplyr::mutate(order = row_number())

ggplot(data = top_words_combined) +
  geom_bar(aes(x = Count, y = as.factor(order)), stat="identity", fill = "#a4dba4") +
  geom_text(aes(x = 0, y = as.factor(order), label = paste0(word,'  (',Count,")"), hjust = "left"), size = 3) + 
  facet_grid(field ~ def, switch = "y", scales = "free") +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    panel.grid = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    panel.background = element_rect(fill = NA, color = "grey40"),
    axis.title = element_blank()
  )

```

```{r output, echo=FALSE, message=FALSE, warning=FALSE}


# All Visits
write.csv(file = "Output_ThreeDefs/Three Defs All Visits.csv",
          x = three_defs_table,
          row.names = FALSE)

# Def1 only
write.csv(file = paste0("Output_ThreeDefs/",def1_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def1_only==1,],
          row.names = FALSE)

# Def2 only
write.csv(file = paste0("Output_ThreeDefs/",def2_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def2_only==1,],
          row.names = FALSE)

# Def3 only
write.csv(file = paste0("Output_ThreeDefs/",def3_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def3_only==1,],
          row.names = FALSE)

# Def1 and Def2 
write.csv(file = paste0("Output_ThreeDefs/",def1_short," and ",def2_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def1_def2==1,],
          row.names = FALSE)

# Def1 and Def3 
write.csv(file = paste0("Output_ThreeDefs/",def1_short," and ",def3_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def1_def3==1,],
          row.names = FALSE)

# Def2 and Def3 
write.csv(file = paste0("Output_ThreeDefs/",def2_short," and ",def3_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def2_def3==1,],
          row.names = FALSE)

# Def1 matched elements
write.csv(file = paste0("Output_ThreeDefs/",def1_short," Matched Elements.csv"),
          x = def1_elements_detected,
          row.names = FALSE)

# Def2 matched elements
write.csv(file = paste0("Output_ThreeDefs/",def2_short," Matched Elements.csv"),
          x = def2_elements_detected,
          row.names = FALSE)

# Def3 matched elements
write.csv(file = paste0("Output_ThreeDefs/",def3_short," Matched Elements.csv"),
          x = def3_elements_detected,
          row.names = FALSE)


```


___
*The template for this report was created by Sara Chronister (Maricopa County Department of Public Health). For questions, ideas for improvement/collaboration, or attribution, please reach out to <sara.chronister@maricopa.gov>.*





