---
title: "Definition Evaluation: `r params$report$query_title`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: true
---

<!-- Setup -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
**Jurisdiction**: `r params$jurisdiction`  
**Report Created**: `r Sys.Date()`    
**Point of Contact**: `r DefinitionInformation[["Setup"]]$PointOfContact` (`r DefinitionInformation[["Setup"]]$POCEmail`)    
**Organization**: `r DefinitionInformation[["Setup"]]$Organization`


***  
## Definition Information  {.tabset}
  
Inclusion terms and codes are displayed in the table below (exclusion terms are not shown in the table)  

<!-- Definition #1 --> 

`r if(params$n_queries_eval >= 1){paste0('### ',syndrome_eval_list[[1]]$setup$info$Syndrome,' (',syndrome_eval_list[[2]]$setup$info$Abbreviation,')')}`

`r if(params$n_queries_eval >= 1){paste0('**Total Visits Identified:**')}`
`r if(params$n_queries_eval >= 1){syndrome_eval_list[[1]]$analysis$total_pretty}`

`r if(params$n_queries_eval >= 1){paste0('**Query description:**')}`
`r if(params$n_queries_eval >= 1){syndrome_eval_list[[1]]$setup$info$Description}`

`r if(params$n_queries_eval >= 1){paste0('**Full query:**')}`
`r if(params$n_queries_eval >= 1){syndrome_eval_list[[1]]$setup$structure_print}` 

<br>

```{r def1_table, echo=FALSE, message=FALSE, warning=FALSE}

syndrome_eval_list[[1]]$analysis$elements_detected_table %>%
  create_def_component_tables(df=., def_num = 1)

```
  

<!-- Definition #2 --> 

`r if(params$n_queries_eval >= 2){paste0('### ',syndrome_eval_list[[2]]$setup$info$Syndrome,' (',syndrome_eval_list[[2]]$setup$info$Abbreviation,')')}`

`r if(params$n_queries_eval >= 2){paste0('**Total Visits Identified:**')}`
`r if(params$n_queries_eval >= 2){syndrome_eval_list[[2]]$analysis$total_pretty}`

`r if(params$n_queries_eval >= 2){paste0('**Query description:**')}`
`r if(params$n_queries_eval >= 2){syndrome_eval_list[[2]]$setup$info$Description}`

`r if(params$n_queries_eval >= 2){paste0('**Full query:**')}`
`r if(params$n_queries_eval >= 2){syndrome_eval_list[[2]]$setup$structure_print}`

<br>

```{r def2_table, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 2){
  
syndrome_eval_list[[2]]$analysis$elements_detected_table %>% 
    create_def_component_tables(df=., def_num = 2)
}
```


<!-- Definition #3 --> 

`r if(params$n_queries_eval >= 3){paste0('### ',syndrome_eval_list[[3]]$setup$info$Syndrome,' (',syndrome_eval_list[[3]]$setup$info$Abbreviation,')')}`

`r if(params$n_queries_eval >= 3){paste0('**Total Visits Identified:**')}`
`r if(params$n_queries_eval >= 3){syndrome_eval_list[[3]]$analysis$total_pretty}`

`r if(params$n_queries_eval >= 3){paste0('**Query description:**')}`
`r if(params$n_queries_eval >= 3){syndrome_eval_list[[3]]$setup$info$Description}`

`r if(params$n_queries_eval >= 3){paste0('**Full query:**')}`
`r if(params$n_queries_eval >= 3){syndrome_eval_list[[3]]$setup$structure_print}`

<br>

```{r def3_table, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 3){
  
syndrome_eval_list[[3]]$analysis$elements_detected_table %>% 
    create_def_component_tables(df=., def_num = 3)
}
```


<!-- Definition Evaluation --> 

<br><br>

## Definition Evaluation

<!-- Visit Counts --> 
`r if(params$n_queries_eval >= 2){paste0('### Visit Counts')}`

`r if(params$n_queries_eval >= 2){paste0('#### The total number of visits identified by all definitions combined was **',syndrome_eval_list$defs_total_pretty,'**')}`
  
`r if(params$n_queries_eval >= 2){paste0('#### Number and percent of all identified visits captured by each definition:')}`
```{r def_summary, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}
if(params$n_queries_eval >= 2){

  all_def_summary <- syndrome_eval_list[[params$overlap_name]] %>%
  select(all_of(params$queries_abbrev)) %>%
  summarize(across(
    .cols = everything(),
    .fns = ~ sum(.))) %>%
  pivot_longer(., cols = everything(), names_to = "Def", values_to = "Count") %>%
  mutate(Total = syndrome_eval_list$defs_total,
         Percent = round(Count/Total,3),
         Percent.Display = paste0(Percent*100,"%"))

all_def_summary %>%
  ggplot(data=., aes(x = Percent, y = reorder(Def,Percent))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=Count, x = Percent-.01), hjust="top", color = "white", size = 3) +
  geom_text(aes(label=Percent.Display, x = Percent+.01), hjust="bottom", color = "black", size = 3) +
  geom_segment(aes(x = 0, xend = 1, y = 0.4, yend = 0.4)) +
  scale_x_continuous(limits = c(0,1.2), expand = c(0,0), breaks = c(0,.25,.50,.75,1), labels = scales::percent_format()) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")  
}
```


<!-- Definition Overlap --> 
`r if(params$n_queries_eval >= 2){paste0('### Definition Overlap')}`

`r if(params$n_queries_eval >= 2){paste0('#### Table')}`
```{r def_comp_table, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 2){
  
  ## Generate Def Comparison Metrics
  all_def_summary <- syndrome_eval_list[[params$overlap_name]] %>%
  count(Definitions, name = "Visits") %>%
  mutate(Total = syndrome_eval_list$defs_total,
         Percent = paste0(round(Visits/Total,3)*100,"%")) %>%
  replace_na(list(Visits=0, Percent="0%")) %>%
  arrange(desc(Visits))

  ## Generate DT Table
  all_def_summary %>%
    DT::datatable(., class='hover cell-border stripe',
                  caption = "Visits Identified by Unique Combinations of Syndromes",
                  rownames=FALSE, escape = FALSE,
                  filter = "top",
                  extensions = c("Buttons", "KeyTable"),
                  options = list(
                  pageLength = nrow(table), # Set Page Length to Show all Demographic Categories
                  dom='Bfrt', # Source: https://datatables.net/reference/option/dom
                  autowidth = TRUE,
                  keys = TRUE,
                 buttons = list(
                      list(extend = 'colvis', text = 'Filter Columns'),
                      list(extend = 'csv', text = 'Download CSV', filename = 'Definition Overlap Table'),
                      list(extend = 'excel', text = 'Download Excel', filename = 'Definition Overlap Table')
                      )
                    )
                  )
}
```

`r if(params$n_queries_eval >= 2){paste0('#### Venn Diagram (Overlap - Not to Scale)')}`
```{r def_comp_venn, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 2){
 plot(eulerr::venn(syndrome_eval_list[[params$overlap_name]] %>% select(all_of(params$queries_abbrev))), 
      labels = TRUE, legend = list(side = "right"), quantities = TRUE)
}
```

`r if(params$n_queries_eval >= 2){paste0('#### Eulerr Plot (Overlap - to Scale)')}`
```{r def_comp_euler, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 2){
 plot(eulerr::euler(syndrome_eval_list[[params$overlap_name]] %>% select(all_of(params$queries_abbrev))), 
      labels = TRUE, legend = list(side = "right"), quantities = TRUE)
}
```


<!-- Time Series --> 
`r if(params$n_queries_eval == 1){paste0('### Visits Over Time')}`
`r if(params$n_queries_eval >= 2){paste0('### Visits Over Time {.tabset}')}`
Use the slider at the bottom of the figures to adjust the start and end dates visible in the graph(s).   
  
`r if(params$n_queries_eval >= 2){paste0('#### Same Scale')}`
```{r ts_same_scale, echo=FALSE, message=FALSE, warning=FALSE}

## Initiate Plotly Plot
ts_plot_same <- plot_ly()

## Add lines for each definition
for(i in 1:params$n_queries_eval){
  
  ts_plot_same <- ts_plot_same %>%
    add_lines(data = syndrome_eval_list[[i]]$results$timeseries,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = params$report$ts_linecolors[i]))
}
rm(i)

## Adding Layout
ts_plot_same %>%
  layout(
    hovermode = "compare",
    xaxis = list(
      range = c(params$start_date,params$end_date),
      rangeslider = list(type = "date", thickness = 0.1)))
```

`r if(params$n_queries_eval >= 2){paste0('#### Independent Scales')}`
```{r ts_separate_scale, echo=FALSE, message=FALSE, warning=FALSE}
if(params$n_queries_eval >= 2){

  ## Define Storage List
list_ts_plot <- list()

for(i in 1:params$n_queries_eval){
  
  list_ts_plot[[i]] <- plot_ly() %>%
    add_lines(data = syndrome_eval_list[[i]]$results$timeseries,
            x = ~Date, y = ~Visits, name = ~Syndrome,
            line = list(color = params$report$ts_linecolors[i])) %>%
    layout(
    hovermode = "compare",
    xaxis = list(
      range = c(min(params$all_dates$Date),max(params$all_dates$Date)),
      rangeslider = list(type = "date", thickness = 0.1)))
}

switch(params$n_queries_eval,
       subplot(list_ts_plot[[1]]),
       subplot(list_ts_plot[[1]], list_ts_plot[[2]],
               nrows = 2, shareX = TRUE, margin = 0.05),
       subplot(list_ts_plot[[1]], list_ts_plot[[2]], list_ts_plot[[3]], 
               nrows = 3, shareX = TRUE, margin = 0.05))
}
```


<!-- Demographics --> 
`r if(params$n_queries_eval == 1){paste0('### Demographics')}`
```{r prep_demographics_table_data, echo=FALSE, message=FALSE, warning=FALSE}

## 1) Bind Demographic Data Together
df_demo <- switch(params$n_queries_eval,
                  bind_rows(syndrome_eval_list[[1]]$results$clean, .id = "id"),
                  bind_rows(syndrome_eval_list[[1]]$results$clean,
                            syndrome_eval_list[[2]]$results$clean, .id = "id"),
                  bind_rows(syndrome_eval_list[[1]]$results$clean,
                            syndrome_eval_list[[2]]$results$clean, 
                            syndrome_eval_list[[3]]$results$clean, .id = "id"))

df_demo <- df_demo %>%
  pivot_longer(.,
               cols = starts_with("def", ignore.case = FALSE),
               names_to = "Syndrome",
               values_to = "Present") %>%
  filter(!is.na(Present)) %>%
  mutate(Syndrome = case_when(
    Syndrome == 'def1' ~ params$queries[1],
    Syndrome == 'def2' ~ params$queries[2],
    Syndrome == 'def3' ~ params$queries[3],
    TRUE ~ NA))


## 2) Generate gtsummary table & convert to tibble for DT import
demo_table <- df_demo %>%
  tbl_summary(include = all_of(params$report$demographics), by = Syndrome) %>%
  modify_header(label = "Demographic") %>%
  bold_labels() %>%
  as_tibble(.) %>% # Convert gtsummary to tibble Source:https://www.danieldsjoberg.com/gtsummary/reference/as_tibble.gtsummary.html
  mutate(Demographic = str_remove_all(Demographic, pattern = "\\_"))

## 3) Clean Variable Names
names(demo_table) <- str_remove_all(string = names(demo_table), pattern = "\\*")

## 4) Adjust gtsummary structure to have both Demographic (Demographic Category) and Identity (Patient Demographics) vars.
demo_table <- demo_table %>%
  mutate(Demographic_Category = lag(Demographic)) %>%
    filter(rowSums(is.na(.)) <= 2) %>%
  mutate(Demographic_Category = ifelse(!Demographic_Category %in%  params$report$demographics, NA, Demographic),
         Demographic_Category = zoo::na.locf(Demographic_Category)) %>% # Source: https://stackoverflow.com/questions/40334837/how-to-group-data-when-data-are-interspersed-with-group-headers-in-the-same-colu
  select(Demographic_Category, Demographic, everything())

```

```{r demographics_table, echo=FALSE, message=FALSE, warning=FALSE}

## Render DT table
demo_table %>% 
  DT::datatable(., class='hover cell-border stripe',
                caption = paste0("Demographic Comparison of Patients Identified by ",
                                 params$report$query_title," Syndrome(s)"),
                rownames=FALSE, escape = FALSE, 
                filter = "top", 
                width = "100%", height = "100%",
                extensions = c("RowGroup",
                             "Buttons",
                             "ColReorder",
                             "FixedColumns",
                             "FixedHeader",
                             "KeyTable",
                             "Select"), # https://rstudio.github.io/DT/extensions.html
                options = list(
                  pageLength = nrow(table), # Set Page Length to Show all Demographic Categories
                  dom='Blfrt', # Source: https://datatables.net/reference/option/dom
                  autowidth = TRUE,
                  colReorder = TRUE,
                  scrollX = TRUE,
                  fixedColumn = TRUE,
                  fixedHeader = TRUE,
                  keys = TRUE,
                  pageLength = nrow(demo_table),
                  rowGroup = list(dataSrc = 0), # Set Row Group to 1st Var in Data Set (Demographic)
                  columnDefs = list(list(targets = c(0),visible = FALSE)), # # Hide Demographic in table (except for Row Group Headers) # Source: https://stackoverflow.com/questions/75952195/remove-grouping-variable-when-using-rowgroup-extension-in-dt-r-package
                  buttons = list(
                    list(extend = 'colvis', text = 'Filter Columns'),
                    list(extend = 'csv', text = 'Download CSV', filename = 'Demographic Table'),
                    list(extend = 'excel', text = 'Download Excel', filename = 'Demographic Table')
                  )
                )
              )
```


<!-- Text Analysis --> 

<br><br>

## Text Analysis {.tabset}

`r paste0('Top ', params$text_analysis_number_ngrams,' words (unigrams) and phrases (bigrams) for each definition and text analysis field.')`

```{r text_analysis, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}

## Create TM Lists
unigram_list <- list()
bigram_list <- list()


## Text Mine
for(i in 1:params$n_queries_eval){
  
  ## Unigrams
  unigram_list[[i]] <- syndrome_eval_list[[i]]$results$clean %>%
    textmine(df=., 
             variables = params$fields_text_analysis, 
             n_grams = 1, # Unigrams
             metric = "n", 
             top_n = params$text_analysis_number_ngrams, top_n_by_variable = TRUE)
  
  ## Bigrams
  bigram_list[[i]] <- syndrome_eval_list[[i]]$results$clean %>%
    textmine(df=., 
             variables = params$fields_text_analysis,
             n_grams = 2, # Bigrams
             metric = "n", 
             top_n = params$text_analysis_number_ngrams, top_n_by_variable = TRUE)
  
  names(unigram_list)[i] <- names(syndrome_eval_list)[i]
  names(bigram_list)[i] <- names(syndrome_eval_list)[i]
}
rm(i)


## Bind All Text Mining (of Individual Definition(s)) Together
unigrams <- bind_results_tm(listDF = unigram_list, ngram = "Unigram")

bigrams <- bind_results_tm(listDF = bigram_list, ngram = "Bigram")

rm(unigram_list, bigram_list)
```

`r paste0('### Unigrams')`
```{r top_unigrams, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}
unigrams %>% plot_tm(df=.)
```

`r paste0('### Bigrams')`
```{r top_bigrams, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}
bigrams %>% plot_tm(df=.)
```

`r paste0('### Table')`
```{r ngram_table, top_ngrams, echo=FALSE, message = FALSE, warning = FALSE}

n_grams <- bind_rows(unigrams, bigrams) %>% 
  mutate(unit = factor(unit, levels = c("Unigram","Bigram"))) %>%
  arrange(desc(n)) %>%
  select(Syndrome = def, `Unigram or Bigram` = unit, Field = field, `Free-Text` = n_gram, `Number of Occurrences` = n)

n_grams %>%
   DT::datatable(., 
                  class='hover cell-border stripe',
                  caption = paste0("Top ",params$text_analysis_number_ngrams," Free-Text N-Grams (by Field)"),
                  rownames=FALSE, escape = FALSE, 
                  filter = "top", 
                  extensions = c("Buttons", "KeyTable", "FixedHeader"), # https://rstudio.github.io/DT/extensions.html
                  options = list(
                    lengthMenu = list(c(10, 25, 50, -1), c('10', '25', '50', 'All')), # Source: https://stackoverflow.com/questions/67484426/how-can-i-show-all-the-entries-with-datatable-in-r-dt-package
                    dom='Blfrtp', # Source: https://datatables.net/reference/option/dom
                    fixedHeader = TRUE,
                    keys = TRUE,
                    buttons = list(
                      list(extend = 'colvis', text = 'Filter Columns'),
                      list(extend = 'csv', text = 'Download CSV', 
                           filename = paste0("Top ",params$text_analysis_number_ngrams," Free-Text N-Grams (by Field)")),
                      list(extend = 'excel', text = 'Download Excel', 
                           filename = paste0("Top ",params$text_analysis_number_ngrams," Free-Text N-Grams (by Field)"))
                    )
                  )
                )
```
___

*The template for this report was created by Sara Chronister & Tyler Bonnell. For questions or ideas for improvement/collaboration, please [create a new GitHub Issue at our repository](https://github.com/sara-chronister/syndrome-definition-evaluation/issues).*